Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
progressed but not yet finished

We have the following assertions:\\
$
{\displaystyle \alpha''=\alpha\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}\\
s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}}\\~\qquad
\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_1+n_2}^{0}\Post_{4i}} }
\\
\displaystyle{\Pred=
\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\land}\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\Post_{5j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\Big)\\
\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}
$\\
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. \qed
\end{itemize}
\end{proof}

@@

 Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
   have:
\begin{itemize}
 \item  For any open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)}$

@@

\begin{proof} 
($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
Suppose that $\Pred_{s,t}\in \mathcal{R}$ and for any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
 \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x\land  
     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
Moreover, by using Lemma \ref{lem-rel-OT-WOT} we know that:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies
\bigg(\forall i \in [0..n].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}
 \wedge
\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},  \Post_{3i}  }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
\bigg)
\end{mathpar}
where\\
$
s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
\Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$

For the sake of simplicity, we will  restrict $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta_{10}},\Pred_{10},\Post_{10}   }
         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$, since $s=s_{10}$. By  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j \in J_2},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
For each of the weak open transition obtained above, we have the following.
We have $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$, then $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta_{2j}\neq\tau\}, 
(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},t_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}}\right)$

\item 
And similarly, for the third  open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta_3},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
Additionally, we have 
$(s_{21},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$, then $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$
and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
\end{mathpar}
 such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta_{3j}\neq\tau\}, 
(s_{31},t_{x y z}|\Pred_{s_{31},t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s_{21},t_{x y}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{xyz}. \vis{\beta_{3j}}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
     \land\! \alpha_{x y z}\!=\!\tau \land  
     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\shortotimes\Post_{OT_{x y z}}}\right)$

\end{enumerate}
\medskip

Moreover, by applying (\WTTrois)~rule on the resulting $\symb{WOT}$s we have:

@@

\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}

@@

           \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}}\dotcup\gamma_{j x y z}^{j\in J_{x y z}},
		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}}}  
         {t \OTWeakarrow {\alpha_{x y}} t_{x y z}} 

@@

     \land \alpha \!=\! \alpha_{x y} \land  

@@

Recall that we have:\\

@@

$\Post_{OT}=\Post_3\subst{\Post_2\shortotimes\Post_1}$\\
Let's start with the statement:\\

@@

The conjunction of the term $\Pred^2\subst{\Post^1}$ with the both sides of the implication, we get:\\  

@@

     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\shortotimes\Post_{OT_x}}  \\

@@

Note because of the domain independence of the substitution, we have also added the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement. Hence a little rewriting gives:\\

@@

By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the consequent of the corresponding implication given in case 2,  the formula becomes: \\

@@

   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}

@@

Furthermore, the rewriting of the implication  gives:\\

@@

Again because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we have added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.
Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
by the consequent of the corresponding implication given in case 3, we get:\\
$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_x.\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post^1}_{\Post_{OT}}\,\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
Therefore, having $s_{31}=s'$ we can conclude:\\

>>>>

We have the following assertions:\\
$
{\displaystyle \alpha''=\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\!}\\
s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}}\\~\qquad
\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
\\
\displaystyle{\Pred=
\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land}\\ 
~\qquad\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
$\\
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. \qed
\end{itemize}
\end{proof}

@@

 Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
   have:
\begin{itemize}
 \item  For any open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred_{s,t} \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)}$

@@

\begin{proof} 
($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
%and for any open transition $OT$ in $\mathcal{T}_1$:
% \begin{mathpar}
%     \openrule
%         {
%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
%         {s \OTarrow {\alpha} s'}
%\end{mathpar}
%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
% \begin{mathpar}
%    \openrule
%         {
%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
%         {t \OTWeakarrow {\alpha_x} t_x}
%\end{mathpar}
% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
% and  \\
% $\Pred_{s,t} \land \Pred_{OT}\\
% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x\land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose that the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'} \in \WT_1

\end{mathpar}
Moreover, by using Lemma \ref{lem-rel-OT-WOT} we know that:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'} \in \WT_1
         \implies
\bigg(\forall i \in [0..n].\openrule
    {
       \beta_{1ij}^{j\in J_1'},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}_1  \wedge

\openrule
         {
           \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}_1
 \wedge
\forall i \in [0..m].\openrule
         {
           \beta_{3ij}^{j\in J_3'},\Pred_{3i},  \Post_{3i}  }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}_1
\bigg)
\end{mathpar}
where\\
$
s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
\Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$

For the sake of simplicity, we will  restrict $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis, and $s=s_{10}$ the we have $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition in $\mathcal{T}_1$, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
For each of the weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},t_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}}\right)$

\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$ then we have $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$. By
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
\end{mathpar}
 such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},t_{x y z}|\Pred_{s_{31},t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s_{21},t_{x y}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{xyz}. \vis{\beta_{3j}}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
     \land\! \alpha_{x y z}\!=\!\tau \land  
     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\shortotimes\Post_{OT_{x y z}}}\right)$

\end{enumerate}
\medskip     
Based on cases described above by applying (\WTTrois)~rule on the resulting $\symb{WOT}$s we have:

@@

\set{\gamma}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{x y}\subst{\Post_{OT_x}}\\

@@

           \set{\gamma},
		\Pred, \Post}  
         {t \OTWeakarrow {\alpha'_{x y}} t_{x y z}} 

@@

     \land \alpha \!=\! \alpha_{x y}' \land  

@@

Let's start with the hypothesis we have:\\

@@

$\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
Moreover, we have the following the statement:\\

@@

The conjunction of the term $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  

@@

     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\shortotimes\Post_{OT_x}}  \\

@@

Note that we added  the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement, because of the domain independence of the substitution. Hence a little rewriting gives:\\

@@

By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the corresponding implication given in case 2,  the formula becomes: \\

@@

   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}

@@

Furthermore, the rewriting of the formula  gives:\\

@@

Again note that because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we  added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.\\

Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
by the conclusion of the corresponding implication given in case 3, we get:\\
$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_x.\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
